Tokio LAINAC Ene-2020

### 2020-01-23 docs/prestokio2020/castillo20202tokio.Rmd
update pres

---
title: "Tokio LAINAC Ene-2020"
author: ".small[Juan Carlos Castillo <br><br> Departamento de Sociología - UCH / COES <br><br>]"
date: "2do Sem 2019"
output:
  xaringan::moon_reader:
    css: ["https://multinivel.netlify.com/docpres/xaringan_custom/xaringan-themer.css","https://multinivel.netlify.com/docpres/xaringan_custom/progress-bar.css"]
    lib_dir: libs
    nature:
      slideNumberFormat:   |
        <div class="progress-bar-container">
          <div class="progress-bar" style="width: calc(%current% / %total% * 100%)">
          </div>
        </div>
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      beforeInit: "https://multinivel.netlify.com/docpres/xaringan_custom/macros.js"
    seal: false # esto omite title slide automática
---
class: bottom, right, inverse

@@

---
class: roja, middle, center

@@

![](../../input/images/tratoPNUD.png)
---
class: inverse, middle, center

# _¿Se percibe en Chile un cambio en los niveles de desigualdad?_

--

@@

---
class: roja, center, middle

@@

---
class: inverse

>>>>

---
title: "Tokio LAINAC Ene-2020"
author: ".small[Juan Carlos Castillo <br><br> Departamento de Sociología - UCH / COES <br><br>]"
date: "2do Sem 2019"
output:
  xaringan::moon_reader:
    css: ["https://multinivel.netlify.com/docpres/xaringan_custom/xaringan-themer.css","https://multinivel.netlify.com/docpres/xaringan_custom/progress-bar.css","https://cdnjs.cloudflare.com/ajax/libs/animate.css/3.7.0/animate.min.css"]
    lib_dir: libs
    nature:
      slideNumberFormat:   |
        <div class="progress-bar-container">
          <div class="progress-bar" style="width: calc(%current% / %total% * 100%)">
          </div>
        </div>
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      beforeInit: "https://multinivel.netlify.com/docpres/xaringan_custom/macros.js"
    seal: false # esto omite title slide automática
---
class: bottom, right, inverse

@@

---
class: roja, middle, center,slideInRight

@@

![](../../input/images/tratoPNUD.png)
---
class: inverse, center

<br>
<br>
# _¿Se percibe en Chile un cambio en los niveles de desigualdad?_

<br>
--

@@

---
class: roja, center, middle,slideInRight

@@

---
class: inverse,slideInRight
